Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2017-03-10 slides/presentation.tex
presentation improvements

\begin{frame}[fragile]{Hybrid Dynamical System}{Continuous Plant and Digital Controller}

@@

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $\hat{G}(s)$}};
   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.2cm]gs)  {$U(s)$};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.2cm]gs)  {$\hat{Y}(s)$};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=gray!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat {Y}(z)$};\\
   \& \coordinate (aux3);
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

  \path[->] (v1) edge (q1.north);
  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (switch2) edge (q1.west)
   (q1.east) edge (aux1.west)
   (gs.east) edge (switch1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
% \caption{Closed-loop digital control system \label{fig:sampledsystem}}
\end{figure}

@@

\uncover<2->
{
\begin{figure}[ht]
\centering
\tikzset{add/.style n args={4}{
    minimum width=6mm,
    path picture={
        \draw[circle] 
            (path picture bounding box.south east) -- (path picture bounding box.north west)
            (path picture bounding box.south west) -- (path picture bounding box.north east);
        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
        }
    }
 }

@@

\only<2>{
\begin{displaymath}
\label{eq:pulsetf}
\hat{G}(z) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{\hat{G}(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace
\end{displaymath}
}

@@

\only<3>{
\begin{equation*}
\label{eq:outputfunctions}
\hat{Y}(z)=\frac{\nu_{1}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{\nu_{2}(z)\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{R(z)\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}
\end{equation*}
}

\uncover<4>{
Common denominator:
$$\hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z)$$
}

@@

\begin{frame}[fragile]{Our CEGIS Model}
\begin{figure}[htb]
\centering
\resizebox{1.0\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=7cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \only<1,22>{\& \node[ellipse, fill=gray!20] (done) {{\sc Done}};}\\
   \& \\
   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based\\Verifier};
   \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Interval Arithmetic\\Verifier};
   }   
    \\
  };

>>>>

\begin{frame}[fragile]{Cyberphysical System}{Continuous Plant and Digital Controller}

@@

 \only<1>{
 \& \node[rectangle,draw,minimum width=3cm,
	minimum height=1.6cm,] (bbdac) {\sc DAC};
 }
 \only<2->{
   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};} 
     }
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $\hat{G}(s)$}};
   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.2cm]gs)  {$U(s)$};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.2cm]gs)  {$\hat{Y}(s)$};
 \only<1>{
 \& \node[rectangle,draw,minimum width=4cm,
	minimum height=1.6cm,] (bbadc) {\sc ADC};
 }   
 \only<2->{
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=gray!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
   }
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat {Y}(z)$};\\
   \& \coordinate (aux3);
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (yz);
  \path (circle.east) edge (cz);
  \only<1> {
   \path
     (cz.east) edge (bbdac.west)
     (bbdac.east) edge (gs.west);
   \path
      (gs.east) edge (bbadc.west)
      (bbadc.east) edge (aux1.west);
  }
   \only<2->{
  \path[->] (v2) edge (q2.north);
  \path  
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west);
  \path[->] (v1) edge (q1.north);
  \path
   (gs.east) edge (switch1.west)
   (switch2) edge (q1.west)
   (q1.east) edge (aux1.west);
  }
  \path
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
% \caption{Closed-loop digital control system \label{fig:sampledsystem}}
\end{figure}

@@

\uncover<3->
{
\begin{figure}[ht]
\centering
\tikzset{add/.style n args={4}{
    minimum width=6mm,
    path picture={
        \draw[circle] 
            (path picture bounding box.south east) -- (path picture bounding box.north west)
            (path picture bounding box.south west) -- (path picture bounding box.north east);
        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
        }
    }
 }

@@

\only<4>{
\begin{displaymath}
\label{eq:pulsetf}
\hat{G}(z) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{\hat{G}(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace
\end{displaymath}
}

@@

\only<5>{
\begin{equation*}
\label{eq:outputfunctions}
\hat{Y}(z)=\frac{\nu_{1}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{\nu_{2}(z)\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{R(z)\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}
\end{equation*}
}

\uncover<6>{
Common denominator:
$$\hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z)$$
}

@@

\begin{frame}[fragile]{Our CEGIS Model}
\begin{figure}[htb]
\centering
\resizebox{1.0\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=7cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \only<1,22>{\& \node[ellipse, fill=gray!20] (done) {{\sc Done}};}\\
   \& \\
   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search\\ \only<2-15>{$\textcolor{blue}{FP=\mathbb{R}\langle16,24\rangle}$}\only<16->{$\textcolor{blue}{FP=\mathbb{R}\langle20,28\rangle}$}};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based\\Verifier};
   \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Interval Arithmetic\\Verifier};
   }   
    \\
  };
